OpenMPIR

### 2017-09-07 paper.tex
Small internal formatting
Removed 'within syncreg' constructs

\begin{figure*}
\begin{tabular}{| c c c | c c c |}
\hline
 & 
\begin{lstlisting}
int fib(int n) 
{                    // A
  if (n < 2)
    return n;
  else
  {
    int x, y;
    #pragma omp task
      x = fib(n-1);  // B
    #pragma omp task
      y = fib(n-2);  // C
    #pragma omp taskwait
    return (x+y);    // D
  }
}
\end{lstlisting}
& & &
\begin{lstlisting}[language=llvm]
if.end:                                 
  detach within %syncreg, label %det.achd, label %det.cont

det.achd:                                 
  %2 = load i32, i32* %n.addr, align 4
  %sub = sub nsw i32 %2, 1
  %call = call i32 @fib(i32 %sub)
  store i32 %call, i32* %x, align 4
  reattach within %syncreg, label %det.cont

det.cont:                                   
  detach within %syncreg, label %det.achd1, label %det.cont4

det.achd1:                                
  %3 = load i32, i32* %n.addr, align 4
  %sub2 = sub nsw i32 %3, 2
  %call3 = call i32 @fib(i32 %sub2)
  store i32 %call3, i32* %y, align 4
  reattach within %syncreg, label %det.cont4

det.cont4:                                  
  sync within %syncreg, label %sync.continue
\end{lstlisting}
 &  \\
\hline
\end{tabular}

>>>>

\begin{figure*}
\begin{tabular}{| c c c | c c c |}
\hline
 & 
\begin{lstlisting}
int fib(int n) 
{                    // A
  if (n < 2)
    return n;
  else
  {
    int x, y;
    #pragma omp task
      x = fib(n-1);  // B
    #pragma omp task
      y = fib(n-2);  // C
    #pragma omp taskwait
    return (x+y);    // D
  }
}
\end{lstlisting}
& & &
\begin{lstlisting}[language=llvm]
if.end:                                 
  detach label %det.achd, label %det.cont

det.achd:                                 
  %2 = load i32, i32* %n.addr, align 4
  %sub = sub nsw i32 %2, 1
  %call = call i32 @fib(i32 %sub)
  store i32 %call, i32* %x, align 4
  reattach label %det.cont

det.cont:                                   
  detach label %det.achd1, label %det.cont4

det.achd1:                                
  %3 = load i32, i32* %n.addr, align 4
  %sub2 = sub nsw i32 %3, 2
  %call3 = call i32 @fib(i32 %sub2)
  store i32 %call3, i32* %y, align 4
  reattach label %det.cont4

det.cont4:                                  
  sync label %sync.continue
\end{lstlisting}
 &  \\
\hline
\end{tabular}
